Dynamic Transition Analysis with TIMES

### 2020-04-02 doc/2020-03-paper/methods.tex
recalculate cfs
Former-commit-id: cc8ec4c78536283719df2eb736f8a025c7d36d77
Former-commit-id: 7b549f3f08aef305bc3927ae2e8b7c853c161385

\subsection{TIMES Model Description}
Objective function.
Constraints.
CO2 constraint interpolation.
\subsection{Initial condition}

\begin{tabular}{| c | c | c | c | c |}
\hline
\textbf{Scenario}& \textbf{Figures}&\textbf{Conventional}&\textbf{Emerging technologies}&\textbf{New nuclear}\\
                 &             &\textbf{technology}&\textbf{technology}&\textbf{reactors}\\
                  \hline
1               &   &      \greencheck           &         \xmark       &      \greencheck     \\ 
2               &   &      \greencheck           &         \xmark       &         \xmark       \\ 
3               &  &      \greencheck           &      \greencheck     &      \greencheck     \\ 
4               &  &      \greencheck           &      \greencheck     &         \xmark       \\
\hline

\subsection{Existing technology}

@@

\end{tabular}

>>>>

\subsection{TIMES Model Description}
Objective function.
Constraints - CO2 emissions reduction targets, increasing demand, CO2 tax.
Important parameters.
\subsection{Initial condition and constraints}
The initial condition is based on energy generation data from EDMC(-> GLS) for the years 2013 , and emission data for electricity generation from National Carbon Trust.

\begin{tabular}{ c c c c c c c c c c}
\textbf{Year} & \textbf{Coal} & \textbf{LNG} & \textbf{Oil} & \textbf{Nuclear} & \textbf{Hydro} & \textbf{Solar} & \textbf{Wind} & \textbf{Geo} & \textbf{Total} \\
 & \textbf{GWh} & \textbf{GWh} & \textbf{GWh} & \textbf{GWh} & \textbf{GWh} & \textbf{GWh} & \textbf{GWh} & \textbf{GWh} & \textbf{GWh} \\
2013 & 259,514 & 449,271 & 108,135 & 9,302 & 84,885 & 162 & 85 & 2,435 & 913,792 \\
\end{tabular}

\begin{tabular}{ c c c }
\textbf{Year} &  \textbf{Model Emissions} & \textbf{Actual Emissions} \\
 &  \textbf{Mt-CO$_2$-eq.} & \textbf{Mt-CO$_2$-eq.} \\
2013 & 593.6 & 592.4 \\
2013 & 593.6 & 592.4 \\
2013 & 593.6 & 592.4 \\
2013 & 593.6 & 592.4 \\
\end{tabular}

\begin{tabular}{| c | c | c | c | c |}
\hline
\textbf{Scenario}& \textbf{Emerging tech.} & \textbf{New nuclear} \\
                 & \textbf{enabled} & \textbf{enabled} \\
                  \hline
1               &   \xmark       &      \greencheck     \\ 
2               & \xmark       &         \xmark       \\ 
3               &   \greencheck     &      \greencheck     \\ 
4               &   \greencheck     &         \xmark       \\
\hline
\end{tabular}
\subsection{Existing technology}

@@
